StanResultsSummary

### 2020-09-25 Results Archive/StanResultsSummary_relaxedgamma3.Rmd
updated code

---
title: "StanResultsSummary"
author: "Kevin Murgas"
date: "4/24/2020"
output: pdf_document
---
Summary of Stan Model Fit Results: Full-Scale (850K sites)
\newline Relaxed Gamma priors (using relaxed gamma fits with x2 variance)
```{r Setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggpubr)
library(knitr)
```

```{r Load, echo=FALSE, include=FALSE}
setwd("/Users/kevinmurgas/Documents/Data+ project/EPIC data")
load("myFA_bulkonly.Rdata")
load("FullResultsTCGA_relaxedgamma.Rdata")

@@

# plot mu,betaT,sigmaE,sigmaP,sigmaPT,sigmaT
fBG <- function(x, a, m1, s1, m2, s2) a*dnorm(x,m1,s1) + (1-a)*dnorm(x,m2,s2)
pM <- ggplot(data.frame(mu=mu_full$p50), aes(x=mu)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("Mu") + xlim(c(-5,5)) + geom_vline(xintercept=mean(mu_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) fBG(x,0.3557,-3.0675, 0.75214,1.1290, 1.39197)/0.1906566,geom="line",color="red")
pB <- ggplot(data.frame(betaT=betaT_full$p50), aes(x=betaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("BetaT") + xlim(c(-5,5)) + geom_vline(xintercept=mean(betaT_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) dcauchy(x,-0.04051, 0.38660)/0.82336,geom="line",color="red")
pE <- ggplot(data.frame(sigmaE=sigmaE_full$p50), aes(x=sigmaE)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaE") + xlim(c(0,2)) + geom_vline(xintercept=mean(sigmaE_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x,2,2)/0.7357589, geom="line",color="red")
pP <- ggplot(sigma_df, aes(x=sigmaP)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaP") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[1], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 3.4016, 9.5057)/2.3641, geom="line",color="red")
pPT <- ggplot(sigma_df, aes(x=sigmaPT)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaPT") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[2], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 2.5210, 3.2948)/1.0097, geom="line",color="red")
pT <- ggplot(sigma_df, aes(x=sigmaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaT") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[3], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 4.2574, 14.370)/3.0964, geom="line",color="red")

@@

# plot the log sigmas
pP <- ggplot(logsig_df, aes(x=sigmaP)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaP)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[1], linetype="dotted") + theme_bw()  + stat_function(fun=function(x) dgamma(exp(x), 3.4016, 9.5057)/2.3641, geom="line",color="red")
pPT <- ggplot(logsig_df, aes(x=sigmaPT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaPT)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[2], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(exp(x), 2.5210, 3.2948)/1.0097, geom="line",color="red")
pT <- ggplot(logsig_df, aes(x=sigmaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaT)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[3], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(exp(x), 4.2574, 14.370)/3.0964, geom="line",color="red")
# and log ratios
pPPTr <- ggplot(logRatio_df, aes(x=PPTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"P/"*sigma*"PT)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[1], linetype="dotted") + theme_bw()
pPTr <- ggplot(logRatio_df, aes(x=PTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"P/"*sigma*"T)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[2], linetype="dotted") + theme_bw()
pPTTr <- ggplot(logRatio_df, aes(x=PTTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"PT/"*sigma*"T)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[3], linetype="dotted") + theme_bw()

@@

# plot scores of sites along PCA axes
# first just axes 1+2 #geom_bin2d(binwidth=c(0.1,0.1), show.legend=FALSE)
pca_df <- data.frame(pca$scores)
pca_df_thin <- pca_df[sample(1:dim(logsig_df)[1], 60000, replace=F),]
p1<-ggplot(data=pca_df_thin, aes(x=Comp.1, y=Comp.2)) + geom_density2d() + ggtitle("Comp 1 vs 2")
p2<-ggplot(data=pca_df_thin, aes(x=Comp.1, y=Comp.3)) + geom_density2d() + ggtitle("Comp 1 vs 3")
p3<-ggplot(data=pca_df_thin, aes(x=Comp.2, y=Comp.3)) + geom_density2d() + ggtitle("Comp 2 vs 3")
p4<-ggarrange(p1,p2,p3,nrow=1,ncol=3)
print(p4)
```
\newpage
Clustering Analysis: \newline 
```{r clust, echo=FALSE,include=TRUE,error=FALSE,message=FALSE,warning=FALSE,results='asis',fig.keep='all',fig.show='asis',fig.height=4,fig.width=6.5}
cat("\\newline")
print("K-means clustering, 3 clusters:")
ptm<-proc.time()
kclust <- kmeans(logsig_df,3,nstart=5)
print(proc.time()-ptm)
clust <- kclust$cluster

# sigmaP vs sigmaPT
p1 <- ggplot(data=logsig_df[which(clust==1),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="red")
p2 <- ggplot(data=logsig_df[which(clust==2),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="green")
p3 <- ggplot(data=logsig_df[which(clust==3),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="blue")
pPxPT_kclust <- ggplot(data = layer_data(p1), aes(x = x, y = y, fill = fill)) + geom_tile() + geom_tile(data = layer_data(p2)) + geom_tile(data = layer_data(p3)) + scale_fill_identity() + theme_bw() + ggtitle("log-P x log-PT") + xlim(-3,1) + ylim(-3,1) + xlab("sigmaP") + ylab("sigmaPT")

# sigmaP vs sigmaT
p1 <- ggplot(data=logsig_df[which(clust==1),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="red")
p2 <- ggplot(data=logsig_df[which(clust==2),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="green")
p3 <- ggplot(data=logsig_df[which(clust==3),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="blue")
pPxT_kclust <- ggplot(data = layer_data(p1), aes(x = x, y = y, fill = fill)) + geom_tile() + geom_tile(data = layer_data(p2)) + geom_tile(data = layer_data(p3)) + scale_fill_identity() + theme_bw() + ggtitle("log-P x log-T") + xlim(-3,1) + ylim(-3,1) + xlab("sigmaP") + ylab("sigmaT")

# sigmaPT vs sigmaT
p1 <- ggplot(data=logsig_df[which(clust==1),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="red")
p2 <- ggplot(data=logsig_df[which(clust==2),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="green")
p3 <- ggplot(data=logsig_df[which(clust==3),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="blue")
pPTxT_kclust <- ggplot(data = layer_data(p1), aes(x = x, y = y, fill = fill)) + geom_tile() + geom_tile(data = layer_data(p2)) + geom_tile(data = layer_data(p3)) + scale_fill_identity() + theme_bw() + ggtitle("log-PT x log-T") + xlim(-3,1) + ylim(-3,1) + xlab("sigmaPT") + ylab("sigmaT")
pSxS_kclust3 <- ggarrange(pPxT_kclust,pPTxT_kclust,pPxPT_kclust,nrow=2,ncol=2)

cat("\\newline")
print("K-means clustering, 4 clusters:")
ptm<-proc.time()
kclust <- kmeans(logsig_df,4,nstart=5)
print(proc.time()-ptm)
clust <- kclust$cluster

# sigmaP vs sigmaPT
p1 <- ggplot(data=logsig_df[which(clust==1),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="red")
p2 <- ggplot(data=logsig_df[which(clust==2),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="green")
p3 <- ggplot(data=logsig_df[which(clust==3),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="blue")
p4 <- ggplot(data=logsig_df[which(clust==4),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="orange")
pPxPT_kclust <- ggplot(data = layer_data(p1), aes(x = x, y = y, fill = fill)) + geom_tile() + geom_tile(data = layer_data(p2)) + geom_tile(data = layer_data(p3)) + geom_tile(data = layer_data(p4)) + scale_fill_identity() + theme_bw() + ggtitle("log-P x log-PT") + xlim(-3,1) + ylim(-3,1) + xlab("sigmaP") + ylab("sigmaPT")

# sigmaP vs sigmaT
p1 <- ggplot(data=logsig_df[which(clust==1),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="red")
p2 <- ggplot(data=logsig_df[which(clust==2),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="green")
p3 <- ggplot(data=logsig_df[which(clust==3),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="blue")
p4 <- ggplot(data=logsig_df[which(clust==4),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="orange")
pPxT_kclust <- ggplot(data = layer_data(p1), aes(x = x, y = y, fill = fill)) + geom_tile() + geom_tile(data = layer_data(p2)) + geom_tile(data = layer_data(p3)) + geom_tile(data = layer_data(p4)) + scale_fill_identity() + theme_bw() + ggtitle("log-P x log-T") + xlim(-3,1) + ylim(-3,1) + xlab("sigmaP") + ylab("sigmaT")

# sigmaPT vs sigmaT
p1 <- ggplot(data=logsig_df[which(clust==1),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="red")
p2 <- ggplot(data=logsig_df[which(clust==2),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="green")
p3 <- ggplot(data=logsig_df[which(clust==3),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="blue")
p4 <- ggplot(data=logsig_df[which(clust==4),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="orange")
pPTxT_kclust <- ggplot(data = layer_data(p1), aes(x = x, y = y, fill = fill)) + geom_tile() + geom_tile(data = layer_data(p2)) + geom_tile(data = layer_data(p3)) + geom_tile(data = layer_data(p4)) + scale_fill_identity() + theme_bw() + ggtitle("log-PT x log-T") + xlim(-3,1) + ylim(-3,1) + xlab("sigmaPT") + ylab("sigmaT")
pSxS_kclust4 <- ggarrange(pPxT_kclust,pPTxT_kclust,pPxPT_kclust,nrow=2,ncol=2)
pSxS_kclust <- ggarrange(pSxS_kclust3,pSxS_kclust4,nrow=1,ncol=2)
cat("\\newline")
print(pSxS_kclust)
rm(p1,p2,p3,p4,pPxPT_kclust,pPxT_kclust,pPTxT_kclust,pSxS_kclust3,pSxS_kclust4,pSxS_kclust)

cat("\\newline")
print("Fuzzy C-means clustering, 3 clusters:")
library(e1071)
ptm<-proc.time()
cclust <- cmeans(logsig_df,3)
print(proc.time()-ptm)
clust <- cclust$cluster

# sigmaP vs sigmaPT
p1 <- ggplot(data=logsig_df[which(clust==1),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="red")
p2 <- ggplot(data=logsig_df[which(clust==2),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="green")
p3 <- ggplot(data=logsig_df[which(clust==3),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="blue")
pPxPT_cclust <- ggplot(data = layer_data(p1), aes(x = x, y = y, fill = fill)) + geom_tile() + geom_tile(data = layer_data(p2)) + geom_tile(data = layer_data(p3)) + scale_fill_identity() + theme_bw() + ggtitle("log-P x log-PT") + xlim(-3,1) + ylim(-3,1) + xlab("sigmaP") + ylab("sigmaPT")

# sigmaP vs sigmaT
p1 <- ggplot(data=logsig_df[which(clust==1),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="red")
p2 <- ggplot(data=logsig_df[which(clust==2),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="green")
p3 <- ggplot(data=logsig_df[which(clust==3),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="blue")
pPxT_cclust <- ggplot(data = layer_data(p1), aes(x = x, y = y, fill = fill)) + geom_tile() + geom_tile(data = layer_data(p2)) + geom_tile(data = layer_data(p3)) + scale_fill_identity() + theme_bw() + ggtitle("log-P x log-T") + xlim(-3,1) + ylim(-3,1) + xlab("sigmaP") + ylab("sigmaT")

# sigmaPT vs sigmaT
p1 <- ggplot(data=logsig_df[which(clust==1),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="red")
p2 <- ggplot(data=logsig_df[which(clust==2),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="green")
p3 <- ggplot(data=logsig_df[which(clust==3),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="blue")
pPTxT_cclust <- ggplot(data = layer_data(p1), aes(x = x, y = y, fill = fill)) + geom_tile() + geom_tile(data = layer_data(p2)) + geom_tile(data = layer_data(p3)) + scale_fill_identity() + theme_bw() + ggtitle("log-PT x log-T") + xlim(-3,1) + ylim(-3,1) + xlab("sigmaPT") + ylab("sigmaT")
pSxS_cclust3 <- ggarrange(pPxT_cclust,pPTxT_cclust,pPxPT_cclust,nrow=2,ncol=2)

cat("\\newline")
print("Fuzzy C-means clustering, 4 clusters:")
library(e1071)
ptm<-proc.time()
cclust <- cmeans(logsig_df,4)
print(proc.time()-ptm)
clust <- cclust$cluster

# sigmaP vs sigmaPT
p1 <- ggplot(data=logsig_df[which(clust==1),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="red")
p2 <- ggplot(data=logsig_df[which(clust==2),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="green")
p3 <- ggplot(data=logsig_df[which(clust==3),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="blue")
p4 <- ggplot(data=logsig_df[which(clust==4),],aes(x=sigmaP,y=sigmaPT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="orange")
pPxPT_cclust <- ggplot(data = layer_data(p1), aes(x = x, y = y, fill = fill)) + geom_tile() + geom_tile(data = layer_data(p2)) + geom_tile(data = layer_data(p3)) + geom_tile(data = layer_data(p4)) + scale_fill_identity() + theme_bw() + ggtitle("log-P x log-PT") + xlim(-3,1) + ylim(-3,1) + xlab("sigmaP") + ylab("sigmaPT")

# sigmaP vs sigmaT
p1 <- ggplot(data=logsig_df[which(clust==1),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="red")
p2 <- ggplot(data=logsig_df[which(clust==2),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="green")
p3 <- ggplot(data=logsig_df[which(clust==3),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="blue")
p4 <- ggplot(data=logsig_df[which(clust==4),],aes(x=sigmaP,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="orange")
pPxT_cclust <- ggplot(data = layer_data(p1), aes(x = x, y = y, fill = fill)) + geom_tile() + geom_tile(data = layer_data(p2)) + geom_tile(data = layer_data(p3)) + geom_tile(data = layer_data(p4)) + scale_fill_identity() + theme_bw() + ggtitle("log-P x log-T") + xlim(-3,1) + ylim(-3,1) + xlab("sigmaP") + ylab("sigmaT")

# sigmaPT vs sigmaT
p1 <- ggplot(data=logsig_df[which(clust==1),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="red")
p2 <- ggplot(data=logsig_df[which(clust==2),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="green")
p3 <- ggplot(data=logsig_df[which(clust==3),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="blue")
p4 <- ggplot(data=logsig_df[which(clust==4),],aes(x=sigmaPT,y=sigmaT)) + geom_bin2d(binwidth=c(0.1,0.1)) + scale_fill_gradient(low="transparent", high="orange")
pPTxT_cclust <- ggplot(data = layer_data(p1), aes(x = x, y = y, fill = fill)) + geom_tile() + geom_tile(data = layer_data(p2)) + geom_tile(data = layer_data(p3)) + geom_tile(data = layer_data(p4)) + scale_fill_identity() + theme_bw() + ggtitle("log-PT x log-T") + xlim(-3,1) + ylim(-3,1) + xlab("sigmaPT") + ylab("sigmaT")
pSxS_cclust4 <- ggarrange(pPxT_cclust,pPTxT_cclust,pPxPT_cclust,nrow=2,ncol=2)
pSxS_cclust <- ggarrange(pSxS_cclust3,pSxS_cclust4,nrow=1,ncol=2)
cat("\\newline")
print(pSxS_cclust)
rm(p1,p2,p3,p4,pPxPT_cclust,pPxT_cclust,pPTxT_cclust,pSxS_cclust3,pSxS_cclust4,pSxS_cclust)
```

>>>>

---
title: "StanResultsSummary"
author: "Kevin Murgas"
date: "4/30/2020"
output: pdf_document
---
Summary of Stan Model Fit Results: Full-Scale (850K sites)
\newline Relaxed Gamma priors (using relaxed gamma fits with x3 variance)
```{r Setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggpubr)
library(knitr)
```

```{r Load, echo=FALSE, include=FALSE}
setwd("/Users/kevinmurgas/Documents/Data+ project/EPIC data")
load("myFA_bulkonly.Rdata")
load("FullResultsTCGA_relaxedgamma3.Rdata")

@@

# plot mu,betaT,sigmaE,sigmaP,sigmaPT,sigmaT
fBG <- function(x, a, m1, s1, m2, s2) a*dnorm(x,m1,s1) + (1-a)*dnorm(x,m2,s2)
pM <- ggplot(data.frame(mu=mu_full$p50), aes(x=mu)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("Mu") + xlim(c(-5,5)) + geom_vline(xintercept=mean(mu_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) fBG(x,0.3557,-3.0675, 0.75214,1.1290, 1.39197)/0.1906566,geom="line",color="red")
pB <- ggplot(data.frame(betaT=betaT_full$p50), aes(x=betaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("BetaT") + xlim(c(-5,5)) + geom_vline(xintercept=mean(betaT_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) dcauchy(x,-0.04051, 0.5799)/0.54890,geom="line",color="red")
pE <- ggplot(data.frame(sigmaE=sigmaE_full$p50), aes(x=sigmaE)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaE") + xlim(c(0,2)) + geom_vline(xintercept=mean(sigmaE_full$p50), linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x,2,2)/0.7357589, geom="line",color="red")
pP <- ggplot(sigma_df, aes(x=sigmaP)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaP") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[1], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 2.7693, 7.0029)/2.0046, geom="line",color="red")
pPT <- ggplot(sigma_df, aes(x=sigmaPT)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaPT") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[2], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 2.1457, 2.4819)/0.8615, geom="line",color="red")
pT <- ggplot(sigma_df, aes(x=sigmaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.05) + ggtitle("sigmaT") + xlim(c(0,2)) + geom_vline(xintercept=sigmaMeans[3], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(x, 3.3643, 10.430)/2.6129, geom="line",color="red")

@@

# plot the log sigmas
pP <- ggplot(logsig_df, aes(x=sigmaP)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaP)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[1], linetype="dotted") + theme_bw()  + stat_function(fun=function(x) dgamma(exp(x), 2.7693, 7.0029)/2.0046, geom="line",color="red")
pPT <- ggplot(logsig_df, aes(x=sigmaPT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaPT)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[2], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(exp(x), 2.1457, 2.4819)/0.8615, geom="line",color="red")
pT <- ggplot(logsig_df, aes(x=sigmaT)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle("log(sigmaT)") + xlim(c(-5,5)) + geom_vline(xintercept=logsigMeans[3], linetype="dotted") + theme_bw() + stat_function(fun=function(x) dgamma(exp(x), 3.3643, 10.430)/2.6129, geom="line",color="red")
# and log ratios
pPPTr <- ggplot(logRatio_df, aes(x=PPTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"P/"*sigma*"PT)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[1], linetype="dotted") + theme_bw()
pPTr <- ggplot(logRatio_df, aes(x=PTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"P/"*sigma*"T)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[2], linetype="dotted") + theme_bw()
pPTTr <- ggplot(logRatio_df, aes(x=PTTr)) + geom_histogram(aes(y=..ncount..), binwidth=0.1) + ggtitle(expression("log("*sigma*"PT/"*sigma*"T)")) + xlim(c(-5,5)) + geom_vline(xintercept=logRatioMeans[3], linetype="dotted") + theme_bw()

@@

# plot scores of sites along PCA axes
# first just axes 1+2 #geom_bin2d(binwidth=c(0.1,0.1), show.legend=FALSE)
pca_df <- data.frame(pca$scores)
pca_df_thin <- pca_df[sample(1:dim(logsig_df)[1], 60000, replace=F),]
p1<-ggplot(data=pca_df_thin, aes(x=Comp.1, y=Comp.2)) + geom_density2d() + ggtitle("Comp 1 vs 2")
p2<-ggplot(data=pca_df_thin, aes(x=Comp.1, y=Comp.3)) + geom_density2d() + ggtitle("Comp 1 vs 3")
p3<-ggplot(data=pca_df_thin, aes(x=Comp.2, y=Comp.3)) + geom_density2d() + ggtitle("Comp 2 vs 3")
p4<-ggarrange(p1,p2,p3,nrow=1,ncol=3)
print(p4)
```
